\documentclass[12pt,a4paper]{article}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{titlesec}
\usepackage{setspace}
\usepackage{hyperref}
\usepackage{enumitem}

\titleformat{\section}{\large\bfseries}{\thesection.}{0.5em}{}
\titleformat{\subsection}{\normalsize\bfseries}{\thesubsection}{0.5em}{}

\setstretch{1.25}

\begin{document}

\begin{center}
    \vspace*{1cm}
    {\LARGE \textbf{Final Report – Roles and Contributions}}\\[0.5cm]
    {\large Video Game History Project}\\[0.5cm]
    {\large Group Members and Responsibilities}\\[1.5cm]
\end{center}

\section*{Overall Leadership}

\subsection*{Group Leaders}

\textbf{Keri Nikolett Noémi}\\
Niki was one of the group leaders and played an essential role in both organization and technical development. She created the index.html page, which served as the homepage and central hub of the website, and designed the navigation system that connected all pages together. Beyond her coding tasks, Niki coordinated communication between the topic teams, tracked their progress, and ensured that all sections were completed on time. Her attention to detail, planning, and leadership kept the entire project cohesive and well-organized.

\vspace{0.3cm}
\textbf{Kyle Leslie} \\
Kyle was the other leader of the group, developing both the contributors.html and appendix.html pages. With a clear goal of establishing a paralleled workflow and providing support on an individual scale, he regularly checked in on the other members to ensure any speed bumps encountered along the way were quickly resolved. He made sure that all group members were properly credited and that supporting materials were clearly organized. Alongside Niki, Kyle oversaw progress across all teams, regularly checking in to confirm deadlines were met and content remained consistent in structure and tone. His organizational skills and clear communication helped maintain quality and unity throughout the project.
\subsection*{CSS Leaders}

\textbf{Anna Khijo} and \textbf{Victor Janeczko} \\
Anna and Victor collaborated to manage the styling of the entire website. They defined the colour palette, typography, and overall layout system to maintain a consistent and professional visual theme. Anna ensured visual uniformity across pages and resolved layout issues as they arose, while also contributing content to the Arcade Games section. Victor refined the global CSS, improving responsiveness and navigation design. Together, they made the website visually cohesive and user-friendly.

\subsection*{Git Leader}

\textbf{Aayush Singh Patel} \\
Aayush managed the group’s GitHub repository, ensuring that version control and collaboration ran smoothly. He created a structured repository, monitored commits, and resolved merge conflicts when necessary. Aayush also ensured that Git practices were properly followed. In addition to his leadership duties, he contributed to the 3D Games section by writing the History of 3D Games. His technical expertise and support helped the group maintain an efficient workflow.

\section*{Topic Teams}

\subsection*{Topic 1 – HD and Indie Games}

\textbf{Leader: Matteo Di Fede} \\
\textbf{Members:} Thomas Quarantana, Michele Piu, Victor Janeczko \\[0.2cm]
Matteo coordinated the research and writing for the HD and Indie Games section, covering the \emph{Dawn of HD} and \emph{Wii}. He ensured the content was structured clearly and focused on technological and creative independence. Thomas contributed sections on new input methods, the PS4 and Xbox One eras, monetisation shifts, and gaming legacy. Michele wrote about the rise of digital distribution, indie renaissance, and mobile gaming’s casual shift, focusing on accessibility and creativity. Victor created the section on Xbox Live and PlayStation Network, detailing the transformation of online gaming. Together, the team provided a comprehensive view of how HD and indie games reshaped the industry.

\subsection*{Topic 2 – 8-bit and 16-bit Era}

\textbf{Leader: Eric Blatter} \\
\textbf{Members:} Huan Li, Yan Sun \\[0.2cm]
Eric led the research and structure for the 8-bit and 16-bit section, writing the introduction, overview, and key comparisons between consoles. Huan focused on 8-bit technology and its cultural impact, as well as Sega’s contributions during the 16-bit transition. Yan explored Nintendo’s advancements during the 16-bit era, covering game design, technology, and legacy. The section effectively illustrated how these eras laid the groundwork for future gaming innovations.

\subsection*{Topic 3 – Early Home Consoles}

\textbf{Leader: Giacomo Rusconi} \\
\textbf{Members:} Kalinina Jekaterina, Sirvinskaja Ilaria \\[0.2cm]
Giacomo led the Early Home Consoles section, writing the introduction, competitor overview, game design evolution, and cultural impact. Kalinina covered the Atari 2600, focusing on technological innovation and popularity. Ilaria contributed research on the Magnavox Odyssey, exploring economic and cultural consequences of early gaming competition. Their section provided a thorough overview of how the home console market began and evolved.

\subsection*{Topic 4 – Arcade Games}

\textbf{Leader: Wissal Aanbi} \\
\textbf{Members:} Anna Khijo, Yunus Varli, Giacomo Cinventini \\[0.2cm]
Wissal led the Arcade Games section and wrote about technology and game design, highlighting how technical advances shaped the golden age of arcades. Anna contributed the History and Evolution of Arcade Games section, tracing the growth of arcades as both an entertainment and cultural phenomenon. Yunus explored iconic games and their legacy, while Giacomo analysed the cultural and social impact of arcades. Together, they presented a balanced overview of arcade gaming’s influence on the industry.

\subsection*{Topic 5 – 3D Games}

\textbf{Leader: Lorenzo Simone} \\
\textbf{Members:} Giovanni Cirino, Aris Liatsis, Aayush Singh Patel \\[0.2cm]
Lorenzo led the 3D Games section, focusing on science and technology behind 3D development. Giovanni researched and described influential 3D games, while Aris examined the consoles that powered the transition to 3D environments. Aayush contributed the historical overview and ensured integration of the team’s content into the main website through GitHub. This section clearly explained how 3D technology revolutionised both graphics and gameplay.

\subsection*{Topic 6 – Modern and Future Games}

\textbf{Leader: Plattner Yonas} \\
\textbf{Members:} Sesko Nik, Pruneanu Andrei, Giulio Molinaro, Markiian Holovatyi \\[0.2cm]
Yonas coordinated this large section, writing about AI-generated worlds, live services, esports, and graphical realism. Nik focused on mobile gaming, its accessibility, dominance, and the role of mobile AR. Andrei covered cloud gaming and cross-platform play, explaining how these features enhance social and technical integration. Giulio examined the most influential modern games across mobile, VR, and esports categories, while Markiian researched VR and AR experiences, haptic interfaces, and the metaverse. Together, they provided a forward-looking exploration of the current and future gaming landscape.

\section*{Summary}

All members worked collaboratively and contributed significantly to their respective roles. The group leaders ensured clear communication and timely completion of tasks. CSS leaders maintained a cohesive visual identity, while the Git leader managed version control effectively. Topic leaders guided their teams in research, writing, and media selection, and all members met their deadlines with professionalism. The result is a comprehensive, visually cohesive, and informative website that reflects teamwork, creativity, and dedication from every participant. Everyone did a fantastic job overall. 

\end{document}
